%---------------------------------------------------------
\cventry
{Software Development/QA Manager and Software Engineer} % Job title
{Ignite Retail Technology} % Organization
{Twin Falls, Idaho} % Location
{October 2010 - July 2011} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Coordinated the flow of software features through Development, CRM, QA and Support departments.}
		\item {Created new processes to enable all teams to work together more efficiently.}
		\item {Designed and implemented new functionality for the server side loyalty engine.}
		\item {Created testing tools in order to automate testing functions.}
		\item {Supported third party point of sales integrators interfacing into the Kickback Reward Systems infrastructure.}
		\item {Bulk loaded new customers implementing Kickback Reward Systems loyalty at their site.}
		\item {Configured hardware and software at the customer site to interface with the Kickback Reward Systems.}
		\item {Analyzed and corrected defects in the KickBack Rewards Systems loyalty software.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Contract Software Engineer at Control4} % Job title
{Prince, Perelson and Associates} % Organization
{Cottonwood Heights, Utah} % Location
{May 2010 - October 2010} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Created a windows \Csh{} form application to configure Windows Media Center applications using XML configuration files.}
		\item {Queried remote devices to allow user configuration changes via a user interface.}
		\item {Created a Wix based install combining several applications.}
		\item {Refactored common pieces of code into a shared library used by all of the applications.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{Harman Pro Group} % Organization
{Sandy, Utah} % Location
{August 2006 - April 2010} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Worked with System Architect (a HiQNet protocol based device management system) and the engineers of Crown, dbx, JBL, AKG, and BSS to provide functional and user interfaces to configure brand devices.}
		\item {Extended the event log database system.}
		\item {Created an advanced parameter search engine and user interface.}
		\item {Developed a scheduling API and user interface.}
		\item {Converted the \Csh{} form based application to WPF.}
		\item {US Patent us 8,938,675: System for automated generation of audio/video control interfaces. Issued Jan 20, 2015}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{LANDesk Software} % Organization
{South Jordan, Utah} % Location
{March 2003 - August 2006} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Worked with a team of developers to create Linux/Unix version of LANDesk Server Manager, a browser based system management product for Intel servers.}
		\item {Designed and implemented shared libraries and executables to interact with monitored hardware using the cross platform \Cpp{} framework.}
		\item {Implemented IPMI Serial Over LAN functionality in \
			\Cpp{}.}
		\item {Designed and wrote the LANDesk Server Manager install in Python with a GTK user interface.}
		\item {Ported C/C++ security components to HPUX and created the packaging for those components.}
		\item {Implemented hardware detection and Server Manager monitoring components for Mac OS X using a combination of \Cpp{} and Objective C.}
	\end{cvitems}
}

%\cventry
%{Software Engineer}
%{Tek Systems}
%{Murray, Utah}
%{August 2003 - November 2003}
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Part of a development team creating Linux/Unix version of LANDesk Server Manager, a browser based system management product.}
%		\item {Developed the LANDesk Server Manager install in python with a GTK GUI.}
%		\item {Designed and implemented utilities in \Cpp{} to interact with monitored hardware and encode/decode obfuscated data.}
%	\end{cvitems}
%}

\cventry
{Software Engineer, Level II} % Job title
{Novell, Inc.} % Organization
{Provo, Utah} % Location
{January 2001 - November 2003} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Ported NICI (Novell International Cryptographic Infrastructure) and NMAS (Novell Modular Authentication System) to Linux, Solaris and AIX.}
		\item {Took part in construction of a build management system which has been used throughout Novell to port products to Linux and Unix systems.}
		\item {Developed product solutions on multiple platforms; Successfully handled product versioning and packaging according to platform; Performed calculation of data authentication code for NICI.}
		\item {Designed, installed, configured and administrated a Unix lab for product development and testing.}
		\item {Designed, implemented, tested and shipped an NMAS method that authenticated users to eDirectory using Kerberos authentication to any Kerberos version V KDC.}
		\item {Enhanced and extended NICI and NMAS products.}
	\end{cvitems}
}

\cventry
{Senior Development Programmer} % Job title
{International Business Machines, Inc.} % Organization
{Provo, Utah} % Location
{April 1994 - December 2000} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {As team lead of School Vista II team, created development process used to develop and maintain IBM School Vista II.}
		\item {Designed and implemented activity launching of course ware products for IBM School Vista II in \Cpp{}.}
		\item {Provided level three customer support for IBM products.}
		\item {Installed and administered lab equipment used in development and testing of products.}
		\item {Developer for division defect tracking system. Administered the DB2 server defect database and enhanced the associated defect tracking application. In this capacity I worked with our IT group maintaining all hardware and software for the defect tracking system.}
		\item {Led a team of developers in the creation of a reading tutor that used voice recognition to prompt users written in \Cpp{}.}
		\item {As team leader of a group of engineers, coordinated and implemented error correction of user reported problems.}
		\item {Converted a family of products from network based to standalone.}
		\item {Worked with a development team to design and implement IBM's next educational management system.}
	\end{cvitems}
}
