\cventry
{Principal Software Engineer} % Job title
{Newfold Digital} % Organization
{Salt Lake City, Utah} % Location
{March 2019 - December 2023} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{
			Designed and implemented multiple React components React user interface for promotional sales on the Bluehost website. Designed and implemented supporting backend microservice that served up promotions as they occurred.Implemented python client module so that microservices could extract data from the hosting platform.Designed and implemented with other engineers the targeted content service to service content to specific users when they logged into the hosting platform website. This Django service ran in an Openshift container. Integrated DataDog logging into a Flask microservice.Implemented python client module for hosting platform service. Refactored many micro services from running on Flask to FastAPI micro-service technologies. Created and transitioned micro-services from Openshift V3 to V4. Resolved issues with infrastructure and customer facing systems as they arise. Mentored other engineers and assisted when needed.}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     
	\end{cvitems}
}