%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Spencer}{George}
\mobile{801-369-1012} 
%%% Social
\email{provocamper@gmail.com}
%\homepage{www.posquit0.com}
\github{swgunxdev}
\linkedin{spencer-george-76a05b1}
%%% Optionals
\position{Senior Software Engineer{\enskip\cdotp\enskip}Computer Scientist}
% \quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Recruitment Team}
  {EasyPost}
\letterdate{\today}
\lettertitle{Job Application for Senior Software Engineer}
\letteropening{Dear Sirs,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Spencer George~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
Thank you for the opportunity to apply for the Senior Software Engineer role at your company. After reviewing your job description, it's clear that you're looking for a candidate that is extremely familiar with the responsibilities associated with the role, and can perform them confidently. Given these requirements, I am certain that I have the necessary skills to successfully do the job adeptly and perform above expectations.

\cvparagraph{Why EasyPost?}
I am an adaptable professional who has been consistently praised as quality-oriented by my co-workers and management. Over the course of my 30-year career I have developed the skills directly relevant to the Senior Software Engineer role you are hiring for, including Python, MySQL, Redis, REST, HTTP/HTTPS, containers and scaling. Overall, I have consistently demonstrated problem solving, critical thinking, and multitasking abilities in every aspect of my Senior Software Engineer role at ClearOne, and I invite you to review my detailed achievements in the attached resume.

\cvparagraph{Why Me?}

After reviewing my resume, I hope you will agree that I am the type of competent and competitive candidate you are looking for. I look forward to elaborating on my my specific skills and abilities will benefit your organization. Please contact me at 801-369-1012 or via email at provocamper@gmail.com to arrange for a convenient meeting time.

Thank you for your consideration, and I look forward to hearing from you soon,

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
