%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Spencer}{George}
\address{358 Cherry Drive, Riverdale, UT, 84405, United States of America}
\mobile{801-369-1012} 
%%% Social
\email{swgunxdev@yahoo.com}
%\homepage{www.posquit0.com}
%\github{posquit0}
\linkedin{spencer-george-76a05b1}
%%% Optionals
\position{Senior Software Engineer{\enskip\cdotp\enskip}Security Expert}
\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre  Parkway\\Mountain View, CA 94043}
\letterdate{\today}
\lettertitle{Job Application for Senior Software Engineer}
\letteropening{Dear Mr./Ms./Dr. George,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Spencer George~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter


In university or through your career, describe your achievements that you are particularly proud of.
Teaching myself to program in C with Lightspeed C on my Mac.
Building my own 20 MB hard drive for my Mac 512KE.
Installing Linux kernel 0.99.5 on my pc after using gopher to download the 30 or so 3.5 floppy disks for the slackware distro.
Getting hired by IBM.
Making the decision to learn an shell(bash), interpreted(python_1.7) and compiled(c++) programming language.
Deciding to collect programming languages and learn how to create my own.


How would you describe your level of experience as a professional software engineer?


Describe your Linux administration experience skill and how you have acquired that
As stated earlier I started learning Linux with the installation of very early distros of Slackware on my pc. I learned to deal with partitioning on single and multiple drive systems. Since this was just a home computer I learned to configure dialup so I could connect to the internet. It was not until I got my job at Novell that I really started administrating UNIX boxes. I knew about the differences between Linux and UNIX, but not experienced it yet. A senior software engineer mentored me through the process of maintaining five different UNIX operating systems, which were SunOS, Solaris, DEC Unix, HP/UX, AIX and Linux. Together we assembled a Linux file server for the engineering organization. This server was attached via NFS to by all of development boxes per operating system. We maintained the system for 45 developers and the EDirectory build team for about 1.5 years. 


Describe your Python software development skill and how you have acquired that
I made Python my choice because it is readable, modular, portable, and extensible. I tested the use of Basic, Forth, Perl, Pascal, Modula, Lisp, and Python. Lisp and Perl are too easily unreadable. Basic is well basic. Forth,Pascal, Modula and Lisp were a challenge in finding versions that worked on Mac, Linux, and Windows so I could have portable code. Python was both a choice of testing and I enjoyed using it. 
At LANDesk I was tasked with using Python to create an installer 

Describe your experience with SQL and relational data modeling, and summarize your learning with large-scale database backed applications

Describe your experience of web front-end and back-end development 


What would you like to achieve in career development and skills development?

How are you involved in open source software?


What interests you about working for Canonical?
I would like to 


\begin{cvletter}
\cvparagraph{About Me}
Thank you for the opportunity to apply for the Senior Software Engineer role at your company. After reviewing your job description, it's clear that your're looking for a candidate that is extremely familiar with the responsibilities associated with the role, and can perform them confidently. Given these requirements, I am certain that I have the necessary skills to successfully do the job adeptly and perform above expectations.

\cvparagraph{Why Google?}
I am an adaptable professional who has been consistently praised as quality-oriented by my co-workers and management. Over the course of my 25-year career, I'va developed a skill set directly relevant to the Senior Software Engineer  role you are hiring for, including application development, advanced technology, and server architecture. Overall, I have consistently demonstrated problem-solving, critical thinking, and multitasking abilities in every aspect of my Senior Software Engineer role at ClearOne, and I invite you to review my detailed achievements in the attached resume.

\cvparagraph{Why Me?}

After reviewing my resume, I hope you will agree that I am the type of competent and competitive candidate you are looking for. I look forward to elaborating on my my specific skills and abilities will benefit your organization. Please contact me at(801)369-1012 or via email at swgunxdev@yahoo.com to arrange for a convenient meeting time.

Thank you for your consideration, and I look forward to hearing from you soon,

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
