%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}
\usepackage{pdfpages}
% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Spencer}{George}
\mobile{801-369-1012} 
%%% Social
\email{provocamper@gmail.com}
%\homepage{www.posquit0.com}
\github{swgunxdev}
\linkedin{spencer-george-76a05b1}
%%% Optionals
\position{Senior Software Engineer{\enskip\cdotp\enskip}Computer Scientist}
% \quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Recruitment Team}
  {Lockheed Martin}

\recipientlogo{spencer/Lockheed_Martin_logo.pdf}
\letterdate{\today}
\lettertitle{Job Application for Senior Software Engineer Level 3}
\letteropening{Dear Sirs,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Spencer George~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\lettersection{About Me}
My name is Spencer George I am , thank you for the opportunity to apply for the Senior Software Engineer Level 3 role at Lockheed Martin. I found this position through LinkedIn. After reviewing the job description, it's clear that the engineering team is looking for an engineer that is familiar with software, firmware and electronics. Advancing sUAS technology such as Indago would be such an awesome position. I have found working on embedded software that can be remotely controlled as an interesting system to work on.  

Over the course of my career I have been writing code in C and \Cpp  at IBM, Novell, LANDesk, and SoftHaven. A side project that I completed was done in C with Arduino microprocessors to simulate duck feeding behavior. In order to verify code I have used automated unit, integration and system testing to improve development velocity and quality. Further tests were completed by writing and executing test plans by myself or others. 

At Harman International and ClearOne I used software simulators and FPGAs as methods of developing audio processing equipment. Oscilloscopes, power supplies, and digital multi-meters where used to provide power and measure input/output of the system. I am familiar with electrical schematics after having taken a college course in solid state electronics.

Although I am not experienced in sUAS, I am familiar with RC aircraft. I have cloned the Ardupilot repository and built the code so that I can expand my knowledge of working with autonomous devices and the planning software. This is an area of engineering that I am excited and enthralled to learn. I am certain that I have the necessary skills to successfully do the job adeptly and perform above expectations.

\lettersection{Why Lockheed Martin?}
I am an adaptable professional who has been consistently praised as quality-oriented by my co-workers and management. Over the course of my 30-year career I have developed the skills directly relevant to the Senior Software Engineer role you are hiring for, including C, \Cpp, and Python. Overall, I have consistently demonstrated problem solving, critical thinking, and multitasking abilities in every aspect of my Senior Software Engineer role at Lockheed-Martin, and I invite you to review my detailed achievements in the attached resume.

\lettersection{Why Me?}
After reviewing my resume, I hope you will agree that I am the type of competent and competitive candidate you are looking for. I look forward to elaborating on my my specific skills and abilities will benefit your organization. Please contact me at 801-369-1012 or via email at provocamper@gmail.com to arrange for a convenient meeting time.

Thank you for your consideration, and I look forward to hearing from you soon,

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}


% Senior Software Engineer - Level 3
%Aeronautics Company
%Utah
%661199BR

%As a seasoned Senior Software Engineer with a strong background in backend development, I am excited to apply for the Senior Software Engineer, Backend position at magic. With my extensive experience in designing and implementing complex systems, I am confident in my ability to contribute effectively to your team.
%
%Throughout my career, I have successfully led projects at reputable companies such as SoftHaven, Newfold Digital, Upwell, and ClearOne. My expertise in backend technologies, including FastAPI, Django, and REST APIs, aligns well with the requirements of the role at magic. I have a proven track record of developing scalable solutions, managing databases like PostgreSQL, and integrating various services to enhance overall system performance.
%
%Moreover, my proficiency in DevOps tools such as AWS, Docker, and Kubernetes will enable me to streamline deployment processes and ensure seamless operations at magic. I am committed to staying updated with the latest technologies and have recently obtained certifications in Kubernetes administration and AWS solutions architecture to further enhance my skill set.
%
%I am excited about the opportunity to bring my technical skills, leadership experience, and passion for innovation to the team at magic. I am confident that my background and expertise make me a strong candidate for the Senior Software Engineer, Backend position, and I look forward to the possibility of contributing to your dynamic team.